\documentclass[letterpaper,11pt]{article}

% -------------------------
% PACKAGES
% -------------------------
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[default]{lato}
\input{glyphtounicode}

% -------------------------
% MARGINS
% -------------------------
\usepackage[left=0.50in,right=0.50in,top=0.50in,bottom=0.50in]{geometry}

% -------------------------
% PAGE STYLE
% -------------------------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\pdfgentounicode=1

% -------------------------
% TYPOGRAPHY / HIERARCHY
% -------------------------
\titleformat{\section}{
  \vspace{-14pt}\bfseries\Large\raggedright
}{}{0em}{}[\color{black}\titlerule\vspace{-7pt}]

\setlist[itemize]{
  leftmargin=1.2em,
  labelsep=0.4em,
  topsep=0pt,
  itemsep=1pt,
  parsep=0pt,
  partopsep=0pt
}

\newcommand{\roleline}[2]{%
  \textbf{\large #1}\hfill{\small #2}\\[-2pt]
}
\newcommand{\orgline}[1]{%
  {\small\textit{#1}}\\[-3pt]
}
\newcommand{\bulletsstart}{\begin{itemize}\footnotesize}
\newcommand{\bulletsend}{\end{itemize}}

\begin{document}

% -------------------------
% HEADER
% -------------------------
\begin{center}
{\LARGE \textbf{Cynthia Wang}}\\[-2pt]
{\normalsize \textit{QA Tester @ Elections Canada}}\\[-3pt]
{\small
\href{mailto:cynthia.wang812@gmail.com}{cynthia.wang812@gmail.com} \textbullet{}
Ottawa, ON \textbullet{}
\href{https://github.com/cynw22}{GitHub} \textbullet{}
\href{https://www.linkedin.com/in/cynthia-wang-7b9290298}{LinkedIn} \textbullet{}
\href{https://cynw22.github.io/Portfolio2/}{Portfolio}
}
\end{center}

% -------------------------
% TECHNICAL SKILLS
% -------------------------
\section{Technical Skills}
{\small
\textbf{QA \& Testing:} Test case execution, defect tracking, regression testing, Agile/Scrum, structured documentation \\
\textbf{Government Tools:} EFR (Electronic Financial Return), EC Connex, FRMS, GCDocs, Power PDF Advanced, VMware \\
\textbf{Programming:} C/C++, Python, JavaScript, HTML/CSS, SQL \\
\textbf{Design \& UX:} Figma, Adobe XD, Illustrator, Photoshop, InDesign, Premiere Pro, After Effects; wireframing, prototyping, personas, usability testing \\
\textbf{Game \& 3D:} Unity, C\#, Maya, Blender \\
\textbf{Research:} Interviews, questionnaires, observation, sentiment \& thematic analysis, trend analysis, report writing
}

% -------------------------
% EXPERIENCE
% -------------------------
\section{Experience}

\roleline{Student Tester}{Jan 2025 -- Present}
\orgline{Elections Canada --- Gatineau, QC}
\bulletsstart
  \item Executed 300+ Electronic Financial Return (EFR) test cases; identified system issues and improved reliability through detailed analysis and defect documentation.
  \item Maintained EC Connex and FRMS records for accurate data entry and reporting; captured detailed test documentation in Word and Power PDF Advanced.
  \item Tracked defects through to resolution and partnered with cross-functional teams on fix validation.
\bulletsend

\roleline{Piano Teacher}{Oct 2024 -- Jul 2025}
\orgline{Barrhaven Music Academy --- Ottawa, ON}
\bulletsstart
  \item Delivered weekly lesson plans for 20+ students (ages 4--20); improved RCM pass rates by 15\% and held 80\% retention.
\bulletsend

% -------------------------
% PROJECTS
% -------------------------
\section{Projects}

\roleline{Wonderland Wayfarers --- Capstone (shipped on itch.io)}{Sep 2025 -- Apr 2026}
\orgline{Spiral Eye Studios --- Unity / C\#}
\bulletsstart
  \item Shipped a Unity visual novel (8 endings, 3 mini-games, relationship tracker) about two sisters escaping Wonderland; owned UX across screens, flow, and feedback.
  \item Designed and coded the in-game hint system that nudges players toward the ending their choices are setting up; integrated item-pickup popups so context appears the moment an item enters inventory.
  \item Contributed to the Spiral Eye Studios team site that hosts the full project breakdown.
\bulletsend

\roleline{UX Research \& Mobility Analysis --- 3-Phase Study}{Sep 2025 -- Dec 2025}
\orgline{Carleton University \& Algonquin College}
\bulletsstart
  \item Ran interviews, questionnaires, and observations with 13 participants; performed sentiment and thematic analysis on qualitative data.
  \item Translated findings into actionable insights; built Figma prototypes (web + mobile) and iterated through multiple rounds of usability testing.
\bulletsend

\roleline{Shepherds of Good Hope --- Site Redesign (QA Lead)}{2023}
\orgline{Carleton University \& Algonquin College --- Team of 3}
\bulletsstart
  \item Led QA on a three-person redesign of the SGOH Foundation site: accessibility pass, visual-consistency audit, and broken-link sweep across every page.
  \item Pushed design improvements from research insights; site UX score improved by 30\%.
\bulletsend

% -------------------------
% EDUCATION
% -------------------------
\section{Education}

\roleline{Carleton University \& Algonquin College}{Apr 2026}
\begin{itemize}\footnotesize
  \item Bachelor of Information Technology --- Interactive Multimedia \& Design
\end{itemize}

% -------------------------
% AWARDS, CERTIFICATIONS, LANGUAGES
% -------------------------
\section{Certifications \& Languages}
{\footnotesize
\textbf{Certifications:} TCPS 2: CORE 2022 Research Ethics (2024); Police Record Check Level 3 --- Vulnerable Sector (2024). \\
\textbf{Languages:} English (Fluent); Mandarin, French (Intermediate); Korean, Japanese (Beginner).
}

\end{document}
